My title

### 2021-03-11 outputs/paper/paper.Rmd
Update paper so that appendix numbering works
Add cross-references example

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

@@

@@

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

@@

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

\appendix

@@

# Additional details
